---
title: "TIDAL R Package Vignette"
author: "Amelia Edmondson-Stait"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TIDAL R Package Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The aim is for this digital tool to facilitate trajectories work and remove barriers to implementing longitudinal research to researchers without specialist statistical backgrounds.

# Installation

You can install the package from CRAN using the following R code:

```{r installation}
# install.packages("TIDAL")
```

# Loading the Package
```{r}
# library(TIDAL)
```

# Example Useage

To run the R Shiny application from your local environment:

```{r}
# Open an interactive Shiny GUI:
# launchTIDAL()

# The argument "display" is a character vector and is either "default" or "browser". Default is "default".
# "default" opens the Shiny app in a pop-out window in RStudio, while "browser" opens it in a web browser.

# Launch Shiny app in a pop-out window in RStudio
# launchTIDAL(display = "default")

# Launch Shiny app with browser display
# launchTIDAL(display = "browser")

```



