---
title: "TIDAL Code"
output: html_document
---

```{r setup, echo = FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tidyr)
library(lme4)
library(ggplot2)
library(broom.mixed)
library(tibble)
library(stringr)
library(car)
library(multcomp)
```

# Introduction {.tabset}
This script is to demonstrate some of the code that happens in the background of the application, using the simulated dataset and a simple linear model.

## Data Formatting

### Upload data in wide format and convert to long format
```{r}
# Load in wide format dataframe
dataWide <- read.csv("../data/emot_reg_emot_simulated.csv")

# Gather sdq_t columns into long format (this is a questionnaire score at each time point)
dataScore <- dataWide %>%
                gather(score_cat_test_col, score, all_of(c("sdq_t1", "sdq_t2", "sdq_t3", "sdq_t4", "sdq_t5"))) 

# Gather age_t columns into long format (this is age at each time point)
dataLong <- dataWide %>%
              gather(time_point, age, all_of(c("age_t1", "age_t2", "age_t3", "age_t4", "age_t5")))

# Merge them into one dataframe
dataLong[,"score"] <- dataScore[,"score"]

# Have a look at the dataframe
head(dataLong)

```
## Data Exploration {.tabset}

### Choose variables for modelling
```{r}
# This is similar to the drop down selections on the Data Exploration page.
ID <- "subject"
traj <- "score"
age <- "age"
modelType <- "Linear"
timePoint <- "time_point"
```

```{r}
# Mean center age (this helps the model fit)
dataLong <- dataLong %>%
          mutate(age_original = as.numeric(!!sym(age)) ) %>%
          mutate(!!sym(age) := as.numeric(!!sym(age)) - mean( as.numeric(!!sym(age)), na.rm = T ))
```


### Descriptive Statistics
```{r}
# Table:
dataLong %>%
          group_by(across( !!timePoint )) %>%
          summarise(N = sum(!is.na( !!sym(traj) )),
                    mean = mean(!!sym(traj), na.rm = T),
                    SD = sd(!!sym(traj), na.rm = T),
                    median = median(!!sym(traj), na.rm = T),
                    IQR = IQR(!!sym(traj), na.rm = T)
          )

# Plot
df.plot <- dataLong %>%
          group_by(across( !!timePoint )) %>%
          summarise(Age = mean(age_original, na.rm = T),
                    Phenotype = mean(!!sym(traj), na.rm = T),
                    SD = sd(!!sym(traj), na.rm = T),
                    n = sum(!is.na( !!sym(traj) ))) %>%
          mutate(upper = Phenotype + ( qnorm(0.975)*SD/sqrt(n) ),
                 lower = Phenotype - ( qnorm(0.975)*SD/sqrt(n) ))

ggplot(df.plot,aes(x=Age, y=Phenotype)) +
  geom_point()+
  geom_line() +
  geom_errorbar(aes(ymin = lower, ymax = upper))+
  ylab(paste0("Score (", traj, ")")) +
  xlab("Age")
```

### Model Results

#### Run the model using lme4
```{r}
# Run the model using lmer
fit <- lmer(formula = "score ~ age + (1 + age | subject)",
                          REML=F ,
                          data = dataLong,
                          control=lmerControl(optimizer="bobyqa",
                                              optCtrl=list(maxfun=2e5)))
# Summary of the model:
summary(fit)
```

#### N observations and groups
```{r}
paste0("The number of observations (measurements) is ",
               format(summary(fit)$devcomp$dims[[1]], big.mark=",", scientific=FALSE),
               " and the number of groups (people) is ",
               format(summary(fit)$ngrps[[1]], big.mark=",", scientific=FALSE) ,
               ".")
```

#### Fixed effects
```{r}
cbind(
  tidy(fit, "fixed"),
  confint(fit, "beta_", method = "Wald")) %>%
  mutate(p.z = 2 * (1 - pnorm(abs(statistic)))) %>%
  mutate(p.z = ifelse(p.z <= 0, "p < 0.001", round(p.z, 3)))
```

#### Random effects
```{r}
randomDF <- as.data.frame(VarCorr(fit),
              order = "lower.tri") %>%
              mutate(across(where(is.numeric), round, 3))
colnames(randomDF) <- c("Level", "Variable1", "Variable2", "Variance/Covariance", "SD Variance/Covariance")
randomDF
```

#### Deviance
```{r}
# This is the model fit, you can compare this to similar models.
deviance(fit)
```

### Plot
```{r}
# Add the "prediction"/model col to dataframe (adjustedScore)
# The alternative is to use the "predict" function, but this didn't work when users wanted to add categorical covariates.
# We had to calculate it manually instead. Below is just an example of how you do this for a linear model with no covariates.

ageVec <- dataLong %>% pull(!!age)

coef <- summary(fit)$coefficients

# Calculate the model mean/prediciton. This is age multiplied by the slope plus the intercept.
adjustedScore <- ageVec * coef[2,1] + coef[1,1]

# Add this as a new column to the dataframe
modelDataEdit <- dataLong %>%
                  mutate(pred = adjustedScore)

# Add 95% CIs for these estimates using glht
ageOrig <- dataLong %>% pull(age_original)
ageOrig <- ageOrig[!is.na(ageOrig)]

# Get a vector of the ages we want to calculate 95% CIs for (instead of doing all the ages in the column)
ageCalcs <- c(min(ageOrig), seq(round(min(ageOrig), 1), round(max(ageOrig), 1), 0.5), max(ageOrig) )

# Go through each age and calculate the 95% CI
score_glht <- lapply(ageCalcs, function(x){

    # Get the row names of the coefficients to put in the glht function (this is Intercept and age)
    rowNames <- rownames(summary(fit)$coefficients)
    
    # Round age to 3 decimal places
    ageInput <- round(x - mean(ageOrig), 3)

    # Use glht to get 95% CIs
    # Essentially we are doing the intercept + slope * age == 0 as it is a linear model
    res <- multcomp::glht(fit, linfct = c( paste0(rowNames[1], " + ", rowNames[2], "*", ageInput, " == 0")) )

    # Tidy up the dataframe
    res <- tidy(confint(res))
    rowname <- paste0("Score (", traj, ")")
    res <-  res %>%
              mutate(contrast = paste0(rowname, " (95% CIs)")) %>%
              column_to_rownames(var = "contrast") %>%
              mutate(across(where(is.numeric), round, 2))
          
    return(res)
})

# Put everything into one dataframe
estimate <- do.call(rbind, score_glht) %>%
                      mutate(age = ageCalcs)

# Plot the mean trajectory and it's 95% CIs and the underlying descriptive data:
ggplot() +
          geom_line(data = modelDataEdit, aes(x= age_original ,  y = pred), color = "#1D86C7", linewidth = 1.5, na.rm=T) +
          geom_ribbon(data = estimate, aes(x= age , ymin = conf.low, ymax = conf.high), fill = "#1D86C7", alpha = 0.2, na.rm = T) +
          geom_point(data = df.plot,aes(x=Age, y=Phenotype))+
          geom_line(data = df.plot,aes(x=Age, y=Phenotype)) +
          geom_errorbar(data = df.plot, aes(x=Age, y=Phenotype, ymin = lower, ymax = upper)) +
          ylab(paste0("Score (", traj, ")")) +
          xlab("Age")
```

### Scores at ages
```{r}
# Choose some ages to calculate (these are equivalent to the checkboxes on the app)
ageInput <- c(4, 7, 12)

# Go through each age and let's calculate the score at that age using glht (similar to getting 95% CIs as above)
score <- lapply(as.numeric(ageInput), function(x){

          rowNames <- rownames(summary(fit)$coefficients)

          ageInputRound <- round(x - mean(ageOrig), 3)
        
          # Essentially we are doing the intercept + slope * age == 0 as it is a linear model
          res <- multcomp::glht(fit, linfct = c( paste0(rowNames[1], " + ", rowNames[2], "*", ageInputRound, " == 0")) )

          res <- tidy(confint(res))

          rowname <- paste0("Score (", traj, ")")

          res <-  res %>%
            mutate(contrast = paste0(rowname, " (95% CIs)")) %>%
            column_to_rownames(var = "contrast")
})

# Tidy it up into one dataframe
estimate <- lapply(score, function(df) {
   df %>%
     dplyr::select(estimate)
 })  %>% do.call(cbind, .)

colnames(estimate) <- ageInput
estimate <- estimate %>%
          gather(age, score, 1:ncol(estimate)) %>%
          mutate(age = as.numeric(age))

# Put the CIs into separate dataframes ready for plotting
conf.low <- lapply(score, function(df) {df %>% dplyr::select(conf.low)}) %>% do.call(cbind, .)
colnames(conf.low) <- ageInput
conf.low  <- conf.low %>%
          gather(age, conf.low, 1:ncol(conf.low)) %>%
          mutate(age = as.numeric(age))

conf.high <- lapply(score, function(df) {df %>% dplyr::select(conf.high)}) %>% do.call(cbind, .)
colnames(conf.high) <- ageInput
conf.high  <- conf.high %>%
          gather(age, conf.high, 1:ncol(conf.high)) %>%
          mutate(age = as.numeric(age))%>%
          dplyr::select(-age)

conf <- cbind(conf.low, conf.high, "age")

ggplot() +
  geom_line(data = modelDataEdit, aes(x= age_original ,  y = pred  ) , na.rm=T) +
  theme(legend.text = element_text(color = "black")) +
  geom_errorbar(data = conf, aes(x = age, ymin = conf.low, ymax = conf.high), width = 0.5) +
  geom_point(data = estimate, aes(x = age, y = score), col = "#1D86C7", size = 5) +
  ylab(paste0("Score (", traj, ")")) +
  xlab("Age")

# Tidy up the estimate and 95% CIs to display nicely to the user
estimateCI <- lapply(score, function(df) {
  df %>%
    mutate(estimateCI = paste0(round(estimate,3) , " (", round(conf.low,3) , " - ", round(conf.high,3) , ")")) %>%
    dplyr::select(estimateCI)
})  %>% do.call(cbind, .)
colnames(estimateCI) <- ageInput
estimateCI        
```

### Area under the curve
```{r}
# Choose 2 ages to calculate AUC for (this is the slider on the app)
AUCages <- c(4,10)

# Calculate the AUC for the ages the user has chosen
coef <- summary(fit)$coefficients

ageOrig <- modelDataEdit %>%
              pull(age_original)
ageOrig <- ageOrig[!is.na(ageOrig)]
# Minus mean age so the age is on the same scale as that used in the model
age1 <- AUCages[1] - mean(ageOrig)
age2 <- AUCages[2] - mean(ageOrig)

# Remove any characters that means the deltaMethod function wont work
rowNames <- rownames(coef) %>%
              str_remove_all("I|\\(|\\^|\\)")

# Use the delta method to calculate AUC 
# AUC is calculate by doing age2 (the larger age) * intercept + slope * age2^2/2 minus age1 (the younger age) * intercept + slope * age2^2/2. This is for a linear model.
AUC <- car::deltaMethod(fit, c( paste0("(((", age2, ")*(", rowNames[1], ")) + ((", rowNames[2], ")*(", age2, ")^2/2)) - (((", age1,")*(", rowNames[1], ")) + ((", rowNames[2], ")*(", age1, ")^2/2))") ) , parameterNames = rowNames)

# Format the results
AUC <- paste0( round(AUC$Estimate, 2), " (", round(AUC$`2.5 %`,2), " - ", round(AUC$`97.5 %`,2), ")")

# Plot the results
ggplot() +
          geom_ribbon(data = modelDataEdit,
                      aes(x = age_original, ymax = pred, ymin = 0),
                      alpha = 0.1, show.legend = FALSE, fill = "#1D86C7") +
          geom_line(data = modelDataEdit, aes(x= age_original ,  y = pred ) , na.rm=T)+
          coord_cartesian(xlim = c(AUCages[1], AUCages[2])) +
          scale_colour_discrete(na.translate = F) +
          theme(legend.text = element_text(color = "black")) +
          ylab(paste0("Score (", traj, ")")) +
          xlab("Age") +
          scale_x_continuous(breaks = seq(round(min(modelDataEdit$age_original, na.rm =T)), round(max(modelDataEdit$age_original, na.rm =T)), by = 1),
                             expand = c(0, 0)) +
          scale_y_continuous(expand = c(0, 0))

# Format the results to display to the user
df <- t(data.frame(paste0(AUCages[1], " - ", AUCages[2]),
                     AUC))

rowname <- paste0("AUC (", traj, ") (95% CIs)")
rownames(df) <- c("Age Range", rowname)
df
```
## Interaction Variable {.tabset}

### Choose variable
```{r}
# Demo shown for categorical variable
# Split the trajectory by the sex variable
condition <- "female"

colSplit <- which(colnames(dataLong) %in% condition)

modelData <- dataLong %>%
            filter(!is.na(!!sym(condition))) %>%
            mutate(!!condition := factor( str_replace_all(.[[colSplit]], " |-|/", "_") ) ) 
  

```

### Model Results
```{r}
# Run the model using lmer
fit <- lmer(formula = "score ~ age + female + age*female + (1 + age | subject)",
                          REML=F ,
                          data = modelData,
                          control=lmerControl(optimizer="bobyqa",
                                              optCtrl=list(maxfun=2e5)))
# Summary of the model:
summary(fit)

# Fixed effects
cbind(
            tidy(fit, "fixed"),
            confint(fit, "beta_", method = "Wald")) %>%
            mutate(p.z = 2 * (1 - pnorm(abs(statistic)))) %>%
            mutate(p.z = ifelse(p.z < 0.001, "p < 0.001", round(p.z, 3) ))

# Random effects
randomDF <- as.data.frame(VarCorr(fit),
                        order = "lower.tri") %>%
            mutate(across(where(is.numeric), round, 3))
          colnames(randomDF) <- c("Level", "Variable1", "Variable2", "Variance/Covariance", "SD Variance/Covariance")
          randomDF

```


```{r}
# add the "predicted" column to this dataset (it's not really a prediction because its the same dataset, it just shows the model)

ageVec <- modelData %>% pull(!!age)

coef <- summary(fit)$coefficients

zero <- ageVec * coef[2,1] + coef[1,1]

rowIndex <- which(str_detect(string = row.names(coef),
                             pattern = condition) &
                  str_detect(string = row.names(coef),
                             pattern = ":", negate = T))

rowIndexInteract1 <- which(str_detect(string = row.names(coef),
                                              pattern = condition) &
                                     str_detect(string = row.names(coef),
                                                pattern = ":") &
                                     str_detect(string = row.names(coef),
                                                pattern = "\\^", negate = T))

 n <- length(unique(pull(modelData, !!sym(condition))))
 
 predCovs <- lapply(1:(n-1), function(i){

              coef[1,1] +
              (ageVec * coef[2,1]) +
              coef[rowIndex[i],1] +
              (ageVec * coef[rowIndexInteract1[i],1])
 })

   
num <- str_subset(row.names(coef), condition) %>%
        sub(paste0(".*", condition), "", .) %>%
        unique()

names(predCovs) <- paste0(condition, "_", num)

modelDataEdit <- cbind(modelData, do.call(cbind, predCovs)) %>%
            mutate(zero = zero) %>%
            mutate(!!condition := as.factor(.[[colSplit]]) ) %>%
            mutate(pred =  eval(parse(text =
                                        paste0(paste0("ifelse(", condition, " == '", num, "', ", condition, "_",num,",", collapse = " "), "zero",
                                               paste0(rep(")", length(num)), collapse = ""), collapse = "")
            )))
          
          

head(modelDataEdit, 30)

```

### Plot

```{r}
# use glht to calculate 95% CIs
      
        ageOrig <- modelDataEdit %>% pull(age_original)
        ageOrig <- ageOrig[!is.na(ageOrig)]
        ageCalcs <-  c(min(ageOrig), seq(round(min(ageOrig), 1), round(max(ageOrig), 1), 0.5), max(ageOrig) )

       CI_glht  <- lapply(ageCalcs, function(x){

          n <- length(unique(pull(modelDataEdit, !!sym(condition))))


          rowIndex <- which(str_detect(string = row.names(summary(fit)$coefficients),
                                       pattern = condition) &
                              str_detect(string = row.names(summary(fit)$coefficients),
                                         pattern = ":", negate = T))

          rowNames <- rownames(summary(fit)$coefficients)

          ageInput <- round(x - mean(ageOrig), 3)

              equations <- sapply(1:(n-1), function(i){
                paste0(rowNames[1], " + \`", rowNames[2], "\`*", ageInput, " + \`", rowNames[rowIndex[i]] , "\` + \`", rowNames[2], ":", rowNames[rowIndex[i]],"\`*",ageInput , " == 0")
              })
          res <- multcomp::glht(fit, linfct = c( paste0(rowNames[1], " + \`", rowNames[2], "\`*", ageInput, " == 0"), equations) )
          
          # Tidy results dataframe and rename rows/columns
          res <- tidy(confint(res))

          rowname <- paste0("Score (", traj, ")")
          
          levelNames <- as.character(levels(as.factor(pull(modelDataEdit, !!sym(condition)))))

            res <-  res %>%
              mutate(condition = levelNames)
          
            })

        ageOrig <- modelDataEdit %>% pull(age_original)
        ageOrig <- ageOrig[!is.na(ageOrig)]
        ageCalcs <-  c(min(ageOrig), seq(round(min(ageOrig), 1), round(max(ageOrig), 1), 0.5), max(ageOrig) )
        levelNames <- as.character(levels(as.factor(pull(modelDataEdit, !!sym(condition)))))

        estimate <- do.call(rbind, CI_glht) %>%
          mutate(age = rep(ageCalcs, each = length(levelNames)) ) 

```

```{r}
ggplot() +
              geom_line(data = modelDataEdit, aes(x= age_original ,  y = pred, color = !!sym(condition) ) , na.rm=T) +
              geom_ribbon(data = estimate ,
                          aes(x= age , ymin = conf.low, ymax = conf.high, fill = condition), alpha = 0.2, na.rm = T, show.legend = FALSE) +
              scale_color_manual(values = c("orange", "blue")) +
              scale_fill_manual(values = c("orange", "blue")) +
              geom_point(data = df.plot,aes(x=Age, y=Phenotype))+
              geom_line(data = df.plot,aes(x=Age, y=Phenotype)) +
              geom_errorbar(data = df.plot, aes(x=Age, y=Phenotype, ymin = lower, ymax = upper)) +
              theme(legend.text = element_text(color = "black"))+
              ylab(paste0("Score (", traj, ")")) +
              xlab("Age")
```


### Scores at ages
```{r}
# Select ages to calculate scores for (same as the checkboxes on the app)
ageInputScore <- c(4, 9, 14)

# use glht to calculate scores at ages

ageOrig <- modelDataEdit %>% pull(age_original)
ageOrig <- ageOrig[!is.na(ageOrig)]

score_glht <- lapply(as.numeric(ageInputScore), function(x){


          n <- length(unique(pull(modelDataEdit, !!sym(condition))))


          rowIndex <- which(str_detect(string = row.names(summary(fit)$coefficients),
                                       pattern = condition) &
                              str_detect(string = row.names(summary(fit)$coefficients),
                                         pattern = ":", negate = T))

          rowNames <- rownames(summary(fit)$coefficients)

          ageInput <- round(x - mean(ageOrig), 3)

          equations <- sapply(1:(n-1), function(i){
                paste0(rowNames[1], " + ", rowNames[2], "*", ageInput, " + ", rowNames[rowIndex[i]] , " + ", rowNames[2], ":", rowNames[rowIndex[i]],"*",ageInput , " == 0")
              })
            res <- multcomp::glht(fit, linfct = c( paste0(rowNames[1], " + ", rowNames[2], "*", ageInput, " == 0"), equations) )
 
          # Tidy results dataframe and rename rows/columns
          res <- tidy(confint(res))

          rowname <- paste0("Score (", traj, ")")

          levelNames <- as.character(levels(as.factor(pull(modelDataEdit, !!sym(condition)))))

          res <-  res %>%
            mutate(contrast = paste0(rowname, " [", condition, ", level = ", levelNames, " ] (95% CIs)")) %>%
            column_to_rownames(var = "contrast")
})

# Plot the scores at the given age        
estimate <- lapply(score_glht, function(df) {
            df %>%
              dplyr::select(estimate)
          })  %>% do.call(cbind, .)

colnames(estimate) <- ageInputScore

estimate <- estimate %>%
              gather(age, score, 1:ncol(estimate)) %>%
              mutate(age = as.numeric(age))

conf.low <- lapply(score_glht, function(df) {df %>% dplyr::select(conf.low)}) %>% do.call(cbind, .)
colnames(conf.low) <- ageInputScore
conf.low  <- conf.low %>%
              gather(age, conf.low, 1:ncol(conf.low)) %>%
              mutate(age = as.numeric(age))

conf.high <- lapply(score_glht, function(df) {df %>% dplyr::select(conf.high)}) %>% do.call(cbind, .)
colnames(conf.high) <- ageInputScore
conf.high  <- conf.high %>%
              gather(age, conf.high, 1:ncol(conf.high)) %>%
              mutate(age = as.numeric(age))%>%
              dplyr::select(-age)

conf <- cbind(conf.low, conf.high, "age")

# Plot
ggplot() +
   geom_line(data = modelDataEdit, aes(x= age_original ,  y = pred, color = !!sym(condition) ) , na.rm=T) +
   theme(legend.text = element_text(color = "black")) +
   geom_errorbar(data = conf, aes(x = age, ymin = conf.low, ymax = conf.high), width = 0.5) +
   geom_point(data = estimate, aes(x = age, y = score), col = "#1D86C7", size = 5) +
   ylab(paste0("Score (", traj, ")")) +
   xlab("Age")


# Table
estimateCI <- lapply(score_glht, function(df) {
            df %>%
              mutate(estimateCI = paste0(round(estimate,3) , " (", round(conf.low,3) , " - ", round(conf.high,3) , ")")) %>%
              dplyr::select(estimateCI)
          })  %>% do.call(cbind, .)
colnames(estimateCI) <- ageInputScore
estimateCI


# Difference in scores at ages (with 95% CIs)
levelsScores <- c(0,1)
differenceScores <- lapply(as.numeric(ageInputScore), function(x){
            ageInput <- round(x - mean(ageOrig), 3)

            coef <- summary(fit)$coefficients

            rowIndex <- which(str_detect(string = row.names(coef),
                                         pattern = condition) &
                                str_detect(string = row.names(coef),
                                           pattern = ":", negate = T))

            rowNames <- rownames(coef) %>%
              str_remove_all("I|\\(|\\^|\\)|\\:")

            levelNames <- paste0(condition,levelsScores) %>%
              str_remove_all("I|\\(|\\^|\\)|\\:")

            levelNames1 <- rowNames[str_detect(rowNames, paste0(levelNames, collapse = "|"))]

            res <- deltaMethod(fit, c(paste0(
                  "(", rowNames[1], " + ", rowNames[2], "*", ageInput, " + ", levelNames1[1], " + ", levelNames1[2], "*", ageInput, ") - (",rowNames[1], " + ", rowNames[2], "*", ageInput, ")"
                )), parameterNames = rowNames )

            dif <- paste0( round(res$Estimate, 3), " (", round(res$`2.5 %`,3), " - ", round(res$`97.5 %`,3), ")")
            res <- data.frame(age = dif)
return(res)
})   

difTab <- do.call(cbind, differenceScores)
colnames(difTab) <- ageInputScore
rownames(difTab) <- paste0("Difference between ",levelsScores[1]," and ", levelsScores[2]," (95% CI)")
difTab
                
```

### Area under the curve
```{r}
# Select ages to calculate AUC for (same as the slider bar on the app)
AUCages <- c(4,10)

coef <- summary(fit)$coefficients

ageOrig <- modelDataEdit %>%
          pull(age_original)
ageOrig <- ageOrig[!is.na(ageOrig)]
age1 <- AUCages[1] - mean(ageOrig)
age2 <- AUCages[2] - mean(ageOrig)

rowNames <- rownames(coef) %>%
          str_remove_all("I|\\(|\\^|\\)|\\:")

AUC <- deltaMethod(fit, c( paste0("(((", age2, ")*(", rowNames[1], ")) + ((", rowNames[2], ")*(", age2, ")^2/2)) - (((", age1,")*(", rowNames[1], ")) + ((", rowNames[2], ")*(", age1, ")^2/2))") ) , parameterNames = rowNames)

AUC <- paste0( round(AUC$Estimate, 2), " (", round(AUC$`2.5 %`,2), " - ", round(AUC$`97.5 %`,2), ")")
        
rowIndex <- which(str_detect(string = row.names(summary(fit)$coefficients),
                                   pattern = condition) &
                          str_detect(string = row.names(summary(fit)$coefficients),
                                     pattern = ":", negate = T))

rowIndexInteract1 <- which(str_detect(string = row.names(summary(fit)$coefficients),
                                            pattern = condition) &
                                   str_detect(string = row.names(summary(fit)$coefficients),
                                              pattern = ":") &
                                   str_detect(string = row.names(summary(fit)$coefficients),
                                              pattern = "\\^", negate = T))
      
n <- length(unique(pull(modelDataEdit, !!sym(condition))))

AUCCovs <- lapply(1:(n-1), function(i){
         
            AUC <- deltaMethod(fit,
                               c( paste0(
                                 "(((",age2,")*(",rowNames[1],")) + ((",rowNames[2],")*(",age2,")^2/2) + ((",rowNames[rowIndex[i]],")*(",age2,")) + ((",rowNames[rowIndexInteract1[i]],")*(",age2,")^2/2) ) -
                                   (((",age1,")*(",rowNames[1],")) + ((",rowNames[2],")*(",age1,")^2/2) + ((",rowNames[rowIndex[i]],")*(",age1,")) + ((",rowNames[rowIndexInteract1[i]],")*(",age1,")^2/2) )"
                               ) )
                               , parameterNames = rowNames )

            AUC <- paste0( round(AUC$Estimate, 2), " (", round(AUC$`2.5 %`,2), " - ", round(AUC$`97.5 %`,2), ")")
            AUC
        })
        
AUC_delta <- list(AUC = AUC, AUCCovs = AUCCovs)
       
# Plot
ggplot(data = modelDataEdit) +
            geom_ribbon(data = modelDataEdit,
                        aes(x = age_original, ymax = pred, ymin = 0, fill = !!sym(condition)),
                        alpha = 0.1, show.legend = FALSE) +
            coord_cartesian(xlim = c(AUCages[1], AUCages[2])) +
            geom_line(aes(x = age_original, y = pred, color = !!sym(condition)), na.rm = TRUE) +
            theme(legend.text = element_text(color = "black")) +
            ylab(paste0("Score (", traj, ")")) +
            xlab("Age") +
            scale_x_continuous(breaks = seq(round(min(modelDataEdit$age_original, na.rm =T)), round(max(modelDataEdit$age_original, na.rm =T)), by = 1),
                               expand = c(0, 0))+
            scale_y_continuous(expand = c(0, 0))


# Table
df <- t(
            cbind(
              data.frame(paste0(AUCages[1], " - ", AUCages[2]),
                         AUC_delta$AUC),
              do.call(cbind, AUC_delta$AUCCovs)
            )
)

rowname <- paste0("AUC (", traj, ")")
levelNames <- as.character(levels(as.factor(pull(modelDataEdit, condition))))
rownames(df) <- c("Age Range", paste0(rowname, " [", condition, ", level = ", levelNames, " ] (95% CIs)") )
df
```


```{r}
# -------
# Difference in AUC
levelsAUC <- c(0,1)

levelNames <- paste0(condition,levelsAUC) %>%
          str_remove_all("I|\\(|\\^|\\)|\\:")

coef <- summary(fit)$coefficients

ageOrig <- modelDataEdit %>%
          pull(age_original)
ageOrig <- ageOrig[!is.na(ageOrig)]
age1 <- AUCages[1] - mean(ageOrig)
age2 <- AUCages[2] - mean(ageOrig)

rowNames <- rownames(coef) %>%
          str_remove_all("I|\\(|\\^|\\)|\\:")

levelNames1 <- rowNames[str_detect(rowNames, paste0(levelNames, collapse = "|"))]

res <- deltaMethod(fit, c( paste0(" (( ((",age2,")*(",rowNames[1],")) + ((",rowNames[2],")*(",age2,")^2/2)   + ( (",levelNames1[1],")*(",age2,") ) + ((",levelNames1[2],")*(",age2,")^2/2) ) - ( ((",age1,")*(",rowNames[1],")) + ((",rowNames[2],")*(",age1,")^2/2)   + ( (",levelNames1[1],")*(",age1,") ) + ((",levelNames1[2],")*(",age1,")^2/2) )) - (( ((",age2,")*(",rowNames[1],")) + ((",rowNames[2],")*(",age2,")^2/2) ) - ( ((",age1,")*(",rowNames[1],")) + ((",rowNames[2],")*(",age1,")^2/2)     )) ") ) ,parameterNames = rowNames)
    
dif <- paste0( round(res$Estimate, 2), " 95% CI: (", round(res$`2.5 %`,2), " - ", round(res$`97.5 %`,2), ")")
statement <- paste0("The difference between the two factor levels (for the age ranges ", AUCages[1], " - ", AUCages[2] ,") is ", dif ,".")
statement

```


## {-}

# {-}

